### 2022-01-27 src/text/2-package.tex
Minor cleanup of tex files
Reformat tex files
Run pre commit hook on all files

\section{Gammapy package}
\label{sec:package}

@@

\subsection{Overview}
\begin{figure*}[t]
\centering
\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
\caption{
Gammapy sub-package structure and data analysis workflow.
}
\label{fig:workflow}
\end{figure*}

\subsection{gammapy.data}
The \verb|gammapy.data| sub-package provides access to
DL3 level data and observation handling.

@@

\subsection{gammapy.makers}
\todo{Regis Terrier}
Data reduction

@@

\subsection{gammapy.datasets}
\todo{Atreyee Sinha}
DL4 level data

@@

\subsection{gammapy.modeling}
\todo{Quentin Remy}
Models and fitting

@@

\subsection{gammapy.estimators}
\todo{Axel Donath}
Estimators

\subsection{gammapy.visualisation}
Plotters etc.

\subsection{gammapy.analysis}
\todo{Jose Enrique writes this...}
High level analysis API

\subsection{gammapy.astro}
Dark matter models, source population modelling

\subsection{gammapy.data}
\todo{Cosimo Nigro}

\subsection{gammapy.catalog}
Gamma-ray catalog access

@@

\subsection{gammapy.maps}
\todo{Laura Olivera-Nieto}
The \verb|gammapy.maps| sub-package provides classes for representing pixelized
data structures with at least two spatial dimensions representing a set of
coordinates or a region on a sphere. In addition it allows to handle and arbitray
number of non-spatial data axes, such as time or energy.

@@

    \import{code-examples/generated/}{gp_maps}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{figure}

\subsection{gammapy.irf}
\todo{Fabio Pintore}
IRF classes

\subsection{gammapy.stats}
\todo{Regis Terrier}
Statistics methods

\subsection{gammapy.utils}
Utility functions...

>>>>

\section{Analysis Workflow Overview}
\label{sec:analysis-workflow-overview}

\section{Gammapy package}
\label{sec:gammapy-package}

@@

\subsection{Overview}
\label{ssec:overview}
\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
	\caption{
		Gammapy sub-package structure and data analysis workflow. }
	\label{fig:workflow} \end{figure*}

\subsection{gammapy.data}
\label{ssec:gammapy-data}
The \verb|gammapy.data| sub-package provides access to DL3 level data and
observation handling.

@@

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
\todo{Regis Terrier}
Data reduction

@@

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
\todo{Atreyee Sinha}
DL4 level data

@@

\subsection{gammapy.modeling
\label{ssec:gammapy-modeling}
\todo{Quentin Remy}
Models and fitting

@@

\subsection{gammapy.estimators}
\label{ssec:gammapy-estimators}
\todo{Axel Donath}
Estimators

\subsection{gammapy.visualisation}
\label{ssec:gammapy-visualisation}
Plotters etc.

\subsection{gammapy.analysis}
\label{ssec:gammapy-analysis}
\todo{Jose Enrique writes this...}
High level analysis API

\subsection{gammapy.astro}
\label{ssec:gammapy-astro}
Dark matter models, source population modelling

\subsection{gammapy.data}
\label{ssec:gammapy-data}
\todo{Cosimo Nigro}

\subsection{gammapy.catalog}
\label{ssec:gammapy-catalog}
Gamma-ray catalog access

@@

\subsection{gammapy.maps}
\label{ssec:gammapy-maps}
\todo{Laura Olivera-Nieto}
The \verb|gammapy.maps| sub-package provides classes for representing pixelized
data structures with at least two spatial dimensions representing a set of
coordinates or a region on a sphere. In addition it allows to handle and
arbitray  number of non-spatial data axes, such as time or energy.

@@

\begin{figure}
	\import{code-examples/generated/}{gp_maps}
	\caption{Using gammapy.data to access DL3 level data with a DataStore}
	\label{codeexample:data}
\end{figure}

\subsection{gammapy.irf}
\label{ssec:gammapy-irf}
\todo{Fabio Pintore}
IRF classes

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
\todo{Regis Terrier}
Statistics methods

\subsection{gammapy.utils}
\label{ssec:gammapy-utils}
Utility functions...
